---
title: "Tayssir paper analysis"
output: html_notebook
---
# Setup

```{r set global variables}
rm(list = ls())
NUM_TREES <- 10000
set.seed(99)
```


```{r}
source("Data set-up.R")
source("helpers.R")
```


```{r load data and packages}
library(tidyverse)
library(grf)
library(policytree)
library(mlr)
library(cowplot)
library(magrittr)
library(broom)
library(xtable)

morocco_cont <- read_rds('morocco2.rds')

morocco <- read_rds('morocco2.rds')

morocco_selected <- morocco %>%
  select(
    ends_with("_self"),
    matches("^a.*_1"),
    matches("^[b|f|g|h|j|k]\\d"),
    benef,
    monthly_spending,
    program_knowledge,
    schoolunitid,
    maths_results,
    group,
    hhid
         )

```


```{r define variables}
X_vars <- c('a4_1', 'a13_1', 'monthly_spending', 'a15_1_1', 'a13_self', 'a4_self', 'benef')

Y_vars <- c("maths_results")
```

```{r}
# big_covars <- morocco %>% select(-hhid, -maths_results, -group, -program_knowledge, -schoolid)
```

# Descriptive stats

```{r figure 1 maths scores hist}
morocco %>%
  ggplot(aes(x= maths_results)) +
    geom_histogram(bins = 8) +
    labs(x = "Maths results (sum of normalised components)" , y = "Count") +
    theme_classic()

ggsave("paper_outputs/figure1.png")
```

```{r maths scores by category}
maths <- read_dta("LCT Morroco/cct_aser_an.dta")

results_table <- maths %>%
  select(t6, t5_2, t4_2, t3_2) %>%
  transmute(division = t6 == 1,
            subtraction = t5_2 == 2,
            number_recog = t4_2 ==5,
            digit_recog = t3_2 == 5) %>%
  gather(key = "Indicator", "Score") %>%
  group_by(Indicator) %>%
  mutate(Indicator = factor(Indicator, level = c("digit_recog", "number_recog", "subtraction", "division"), ordered = TRUE)) %>%
  summarise(`Percent perfect` = paste0(round(mean(Score, na.rm = T) * 100,2), "%"))

results_table %>%
  xtable(caption = "Percentage of children receiving a perfect score for each category") %>%
  print(type = "latex", file="paper_outputs/table1.tex")
```

# Analysis for treatment vs control

```{r}
control_forest <- causal_forest (
  morocco_selected %>% 
    select(e1_self:monthly_spending), 
  morocco$maths_results, morocco$group_control,
  num.trees = NUM_TREES,
  clusters = morocco$schoolunitid
  )
```

```{r Just checking we aren't splitting too much on missing variables}
control_ate <- average_treatment_effect(control_forest)
control_ate
```

```{r}
qplot(x = control_forest$predictions) + 
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = control_ate['estimate'], color = "blue") +
  scale_y_continuous(limits = c(0, 600)) +
  annotate("rect", 
           xmin = control_ate['estimate'] - (1.96 * control_ate['std.err']), 
           xmax = control_ate['estimate'] + (1.96 * control_ate['std.err']), ymin = 0, ymax = Inf,
           alpha = .1,fill = "blue") +
  ggtitle("Treatment vs control effect") + 
  labs(x = "Predictions", y = "Counts")

ggsave('paper_outputs/control_plot.png')
```

```{r}
small_forest <- basu_forest(X = morocco_selected %>% 
    select(e1_self:monthly_spending), 
  Y = morocco$maths_results, W = morocco$group_control,
  num.trees = 1000,
  clusters = morocco$schoolunitid,
  num_vars = 30)
```



# Small forest analysis

```{r}
average_treatment_effect(small_forest)
```


# Variable importance analysis

```{r}
all_labels <- joined %>% 
  labelled::get_variable_labels() %>%
  unlist()

test <- get_var_imp(small_forest) %>%
  arrange(desc(Importance))

test$Label <- get_var_labels(baseline1, test$Variable)

test %>% select(Label, Variable, Importance)
```

```{r}
test1 <- get_var_imp(small_forest) %>%
  arrange(desc(Importance))

test1$Label <- get_var_labels(baseline1, test1$Variable)

small_var_imp <- test1 %>% select(Label, Variable, Importance)
```


How do we best think about variable importance instability? There are two forms of error here, Monte Carlo error and sampling error (akin to excess and debiased error originally)

# Plot heterogeneity variables

```{r}
create_cowplot(morocco, X_vars[c(1,2, 4)], 
               var_labels = c("Head gender", "Head age", "Head literacy"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3a.pdf', plot = .)

create_cowplot(morocco, X_vars[c(3, 7)], var_labels = c("Monthly spending", "Beneficiary"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3b.pdf', plot = .)
 
create_cowplot(morocco, X_vars[c(5,6)], var_labels = c("Age", "Gender"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3c.pdf', plot = .)

# Important vars
create_cowplot(morocco, small_var_imp$Variable[1:2], var_labels = c("School fee spend", "'Head's spouse shoes spend"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3d.pdf', plot = .)
 
create_cowplot(morocco, small_var_imp$Variable[3:4], var_labels = c("Expected earnings from primary school", "Head shoes spend"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3e.pdf', plot = .)

create_cowplot(morocco, small_var_imp$Variable[5:6], var_labels = c("Spend on travel", "Child activity between 12:00-12:30"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3f.pdf', plot = .)

create_cowplot(morocco, small_var_imp$Variable[7:8], var_labels = c("Spend on female child shoes", "Amounted donated to mosque"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3g.pdf', plot = .)

create_cowplot(morocco, small_var_imp$Variable[9:10], var_labels = c("Number of days head worked in main activity", "Amount own vegetables consumed"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3h.pdf', plot = .)
```


# Best linear projection

```{r}
  lm_df <- morocco %>%
    select(all_of(X_vars), all_of(small_var_imp$Variable %>% head(15))) %>%
    mutate_all(funs(median_split))
  
  num_missing <- lm_df %>%
    map_int(~.x %>% is.na() %>% sum())
  
  lm_df <- lm_df %>%
    select(which(num_missing < 1000))
  
  lm_df$Y <- small_forest$Y.orig

out_list <- list(
    lm(Y ~ ., data = lm_df %>% select(Y, any_of(X_vars))),
    lm(Y ~ ., data = lm_df %>% select(Y, any_of(small_var_imp$Variable))),
    lm(Y ~ ., data = lm_df)
    )

stargazer(
  out_list,
  type = "html", # You can change this to "latex" for LaTeX output
  title = "Regression Results",
  dep.var.labels = c("Treatment 1", "Treatment 2", "Treatment 3"),
  dep.var.caption = c("Doubly robust scores"),
  column.labels = c("Theoretical variables", "High-importance variables", "Both"),
  dep.var.labels.include = TRUE,
  omit.table.layout = "n", # Omit notes and additional information
  out = "paper_outputs/regression_table_multivariable.htm" # Specify the output file
)
```









# Analysis for labelled vs conditioned

```{r fit control causal forest}

main_forest <- multi_arm_causal_forest (
  morocco_selected %>% 
    select(e1_self:monthly_spending), 
  morocco$maths_results, morocco$group %>% as.factor(),
  num.trees = NUM_TREES,
  clusters = morocco$schoolunitid
  )
```

```{r}
small_forest <- basu_forest(X = morocco_selected %>% 
    select(e1_self:monthly_spending), 
  Y = morocco$maths_results, W = morocco$group %>% as.factor(),
  num.trees = NUM_TREES,
  clusters = morocco$schoolunitid,
  iters = 3)
```


```{r}
main_ate <- average_treatment_effect(main_forest)
main_plots <- map(1:length(main_ate$contrast), function(x) {
  ate_est <- main_ate[x,][c("estimate", "std.err")] %>% unlist()
  preds <- main_forest$predictions[,x]
  qplot(x = preds) + 
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = ate_est['estimate'], color = "blue") +
    scale_y_continuous(limits = c(0, 600)) +
    annotate("rect", 
             xmin = ate_est['estimate'] - (1.96 * ate_est['std.err']), 
             xmax = ate_est['estimate'] + (1.96 * ate_est['std.err']), ymin = 0, ymax = Inf,
             alpha = .1,fill = "blue") +
    ggtitle("Contrast ", paste0(main_ate$contrast[x])) + 
    labs(x = "Predictions", y = "Counts")
})
save_plot('paper_outputs/figure2.png', cowplot::plot_grid(plotlist = main_plots), base_height = 5)
```
# Small forest analysis

```{r}
main_forest <- small_forest
average_treatment_effect(small_forest)
```

```{r}
indiv_ate <- average_treatment_effect(small_forest)
indiv_plots <- map(1:length(indiv_ate$contrast), function(x) {
  ate_est <- indiv_ate[x,][c("estimate", "std.err")] %>% unlist()
  preds <- small_forest$predictions[,x]
  qplot(x = preds) + 
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = ate_est['estimate'], color = "blue") +
    scale_y_continuous(limits = c(0, 600)) +
    annotate("rect", 
             xmin = ate_est['estimate'] - (1.96 * ate_est['std.err']), 
             xmax = ate_est['estimate'] + (1.96 * ate_est['std.err']), ymin = 0, ymax = Inf,
             alpha = .1,fill = "blue") +
    ggtitle("Contrast ", paste0(indiv_ate$contrast[x])) + 
    labs(x = "Predictions", y = "Counts")
})
save_plot('paper_outputs/contrasts.png', cowplot::plot_grid(plotlist = indiv_plots), base_height = 5)
```


# Variable importance analysis

```{r}
all_labels <- joined %>% 
  labelled::get_variable_labels() %>%
  unlist()

test <- get_var_imp(main_forest) %>%
  arrange(desc(Importance))

test$Label <- get_var_labels(baseline1, test$Variable)

test %>% select(Label, Variable, Importance)
```

```{r}
test1 <- get_var_imp(small_forest) %>%
  arrange(desc(Importance))

test1$Label <- get_var_labels(baseline1, test1$Variable)

test1 %>% select(Label, Variable, Importance)
```

```{r}
small_forest <- basu_forest(X = morocco_selected %>% 
    select(e1_self:monthly_spending), 
  Y = morocco$maths_results, W = morocco$group %>% as.factor(),
  num.trees = NUM_TREES,
  clusters = morocco$schoolunitid,
  iters = 5)
small_var_imp <- display_variable_imp(small_forest, baseline1)
write_csv(small_var_imp, "paper_outputs/variables_table.csv")
```


How do we best think about variable importance instability? There are two forms of error here, Monte Carlo error and sampling error (akin to excess and debiased error originally)

# Plot heterogeneity variables

```{r}
create_cowplot(morocco, X_vars[c(1,2, 4)], 
               var_labels = c("Head gender", "Head age", "Head literacy"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3a.pdf', plot = .)

create_cowplot(morocco, X_vars[c(3, 7)], var_labels = c("Monthly spending", "Beneficiary"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3b.pdf', plot = .)
 
create_cowplot(morocco, X_vars[c(5,6)], var_labels = c("Age", "Gender"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3c.pdf', plot = .)

# Important vars
create_cowplot(morocco, small_var_imp$Variable[1:2], var_labels = c("School fee spend", "'Head's spouse shoes spend"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3d.pdf', plot = .)
 
create_cowplot(morocco, small_var_imp$Variable[3:4], var_labels = c("Expected earnings from primary school", "Head shoes spend"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3e.pdf', plot = .)

create_cowplot(morocco, small_var_imp$Variable[5:6], var_labels = c("Spend on travel", "Child activity between 12:00-12:30"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3f.pdf', plot = .)

create_cowplot(morocco, small_var_imp$Variable[7:8], var_labels = c("Spend on female child shoes", "Amounted donated to mosque"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3g.pdf', plot = .)

create_cowplot(morocco, small_var_imp$Variable[9:10], var_labels = c("Number of days head worked in main activity", "Amount own vegetables consumed"), as.data.frame(main_forest$predictions)) %>%
  save_plot(filename = 'paper_outputs/figure3h.pdf', plot = .)
```


# Best linear projection

```{r}
blps <- map(get_scores(main_forest) %>% as.data.frame(), function(y) {
  lm_df <- morocco %>%
    select(all_of(X_vars), all_of(small_var_imp$Variable %>% head(15))) %>%
    mutate_all(funs(median_split))
  
  num_missing <- lm_df %>%
    map_int(~.x %>% is.na() %>% sum())
  
  lm_df <- lm_df %>%
    select(which(num_missing < 1000))
  
  lm_df$Y <- y

  list(
    lm(Y ~ ., data = lm_df %>% select(Y, any_of(X_vars))),
    lm(Y ~ ., data = lm_df %>% select(Y, any_of(small_var_imp$Variable))),
    lm(Y ~ ., data = lm_df)
    )
})

stargazer(
  blps,
  type = "html", # You can change this to "latex" for LaTeX output
  title = "Regression Results",
  dep.var.labels = c("Treatment 1", "Treatment 2", "Treatment 3"),
  dep.var.caption = c("Doubly robust scores"),
  column.labels = c("Theoretical variables", "High-importance variables", "Both"),
  dep.var.labels.include = TRUE,
  omit.table.layout = "n", # Omit notes and additional information
  out = "paper_outputs/regression_table_multivariable.htm" # Specify the output file
)
```






